\section{Work Experience}


\subsection{Current}

\begin{itemize}
\item{\cventry{December 2016--Current}{Livermore Computing
    Staff}{Lawrence Livermore National Laboratory}{Livermore,
        CA}{}{Technical project leader for 1) An end-to-end data science
        platform for analyzing performance of HPC applications and
        facilities across Livermore Computing, and 2) A multi-lab
        research effort for exploring hypothetical next-generation
        memory architectures.}}
\end{itemize}

\subsection{Graduate Student Internships}

\begin{itemize}
\item{\cventry{April 2016--December 2016}{Research Intern}{Lawrence
    Livermore National Laboratory}{Livermore, CA}{}{Researched and
        developed an automated data integration tool for combining
        multiple streaming heterogeneous data sources for monitoring
        HPC application and system performance.}}

\item{\cventry{June 2015--September 2015}{Research Intern}{Lawrence
    Livermore National Laboratory}{Livermore, CA}{}{
        Developed tools for collection and distributed
        storage/processing/analysis of performance data from disparate
        information sources.}}

\item{\cventry{June 2014--September 2014}{Research Intern}{Lawrence
    Livermore National Laboratory}{Livermore, CA}{}{Researched
        advanced data analytic methods for identifying memory
        performance bottlenecks in applications and complex memory
        architectures.}}

\item{\cventry{June 2013--September 2013}{Research Intern}{Lawrence
    Livermore National Laboratory}{Livermore, CA}{}{Researched and
        developed visualization and exploratory analysis methods for
        on-node memory access information (Initiated open source
        projects: Mitos and MemAxes)}}
\end{itemize}

\subsection{Other}

\begin{itemize}

\item{\cventry{January 2015--June 2015}{Performance Consultation}{Stratovan Corporation}{Davis, CA}{}{Research/Development for optimizing the performance of Stratovan's segmentation and detection algorithms. Helped them achieve a 4x throughput improvement.}}

\item{\cventry{June 2010--October 2012}{Software Research and Development}{Intel Corporation}{Folsom, CA}{}{Research/Development to showcase the capabilities of heterogeneous computing on Intel integrated GPU and CPU hardware using OpenCL. Created a debugging and analysis tool for OpenCL programs that eventually became the OpenCL Code Builder that is currently shipped with Intel's OpenCL SDK. Co-authored a patent for the hardware-agnostic OpenCL line-by-line debugging capability in Code Builder.}}

\end{itemize}

